Figures

### 2019-04-30 figures/07_model-selection.Rmd
more posterior exploration

```{r brms_stan}
library(brms)
library(tidybayes)

@@

ggplot(data = all_dist) +
  geom_point(aes(x = hu4vzoneid, y = `50%`)) +
  geom_errorbar(aes(ymin = `5%`, ymax = `95%`, x = hu4vzoneid, color = signif)) +
  geom_hline(yintercept = 0) +
  coord_flip()

@@

# pull 2nd level covariate distributions
get_variables(fit2)
# spread_draws(fit, b_Intercept)

plot(fit, pars = "agvpct")

test <- spread_draws(fit, r_hu4vzoneid[hu4vzoneid,term]) %>%
  dplyr::filter(term == "agvpct") %>%
  group_by(hu4vzoneid) %>%
  summarise(agvpct_effect = median(r_hu4vzoneid))
quantile(test$agvpct_effect, c(0.05, 0.5, 0.95))

m <- add_fitted_draws(dt, b_)

spread_draws(fit, Intercept)
spread_draws(fit1, bagvpct[hu4vzoneid,])

ggplot() + 
    stat_lineribbon(data = m, 
                             aes(x = retention_time_yr, 
                                 y = estimate), .prob = c(0.95), 
                    fill = "grey", color = "black", alpha = 0.5)

+ 
    geom_point(data = nes, aes(x = retention_time_yr, 
                               y = p_percent_retention), 
               size = 0.6, color = "black") + 
    scale_x_log10() + ylim(0, 1) +
    scale_fill_discrete("grey") + 
    theme_pred() + 
ylab("P retention") + xlab("Residence time (yr)") + ggtitle("A.")

stat_lineribbon()
stancode(fit1)

m <- tidybayes::recover_types(fit1)

bayes_results = m %>%
  spread_draws()
%>%
  median_qi(estimate = condition_mean) %>%
  to_broom_names() %>%
  mutate(model = "Bayes")
bayes_result

---
loo1 <- loo(fit1)
loo2 <- loo(fit2)
loo_compare(loo1, loo2)  
---

fit <- brm(formula = model_form, data = dt, 
           family = gaussian())

summary(fit2)
marginal_effects(fit2)
conditions <- data.frame(hu4vzoneid = unique(dt$hu4vzoneid)[1])
rownames(conditions) <- unique(dt$hu4vzoneid)[1]
me_zone <- marginal_effects(fit, conditions = conditions, 
                            re_formula = NULL, method = "predict")
ran_ef <- as.data.frame(ranef(fit)$hu4vzoneid) %>%
  mutate(zoneid = rownames(.)) %>%
  dplyr::filter(zoneid == unique(dt$hu4vzoneid)[1])

plot(me_zone, ncol = 1)$agvpct + 
  ggtitle(unique(dt$hu4vzoneid)[1]) +
  geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
                broom::tidy(fit)$estimate[1])

>>>>

```{r brms_stan}
library(brms)
library(tidybayes)
library(modelr)

@@

ggplot(data = all_dist) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  geom_hline(yintercept = 0) +
  coord_flip()

@@

# pull 2nd level covariate distributions
coef_signif <- bind_rows(
  spread_draws(fit2, b_bagvpct_soybeans) %>%
    do(tibble::as_tibble(t(quantile(.$b_bagvpct_soybeans, 
                                    c(0.05, 0.5, 0.95))))), 
  spread_draws(fit2, b_bagvpct_phosphorusvfertilizervuse) %>%
    do(tibble::as_tibble(t(quantile(.$b_bagvpct_phosphorusvfertilizervuse, 
                                    c(0.05, 0.5, 0.95)))))
  )
coef_signif$var <- c("soybeans", "pfertilizer")

ggplot(data = coef_signif) +
  geom_pointrange(aes(x = var, y = `50%`, ymin = `5%`, ymax = `95%`)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  coord_flip()

# plot prediction lines
# hu4_signif$ZoneID
hu4_id               <- hu4_signif$ZoneID[3]
conditions           <- data.frame(hu4vzoneid = hu4_id)
rownames(conditions) <- hu4_id

me_zone <- marginal_effects(fit1, conditions = conditions, 
                            re_formula = NULL, method = "predict")

ran_ef <- as.data.frame(ranef(fit1)$hu4vzoneid) %>%
  mutate(zoneid = rownames(.)) %>%
  dplyr::filter(zoneid == hu4_id)

plot(me_zone, ncol = 1)$agvpct + 
  geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
                broom::tidy(fit)$estimate[3]) + 
  ggtitle(hu4_id)

ggplot() + 
    geom_point(data = dplyr::filter(dt, 
                                  hu4vzoneid == hu4_id), 
             aes(x = agvpct, y = tp)) + 
  geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
                broom::tidy(fit)$estimate[3])

dt %>%
  modelr::data_grid(agvpct = seq_range(agvpct, n = 101)) %>%
  mutate(hu4vzoneid = hu4_id[1]) %>%
  add_predicted_draws(fit) %>%
  ggplot(aes(x = agvpct, y = tp)) +
  stat_lineribbon(aes(y = .prediction), .width = c(.99, .95, .8, .5), color = "#08519C") +
  geom_point(data = dplyr::filter(dt, hu4vzoneid == hu4_id[1]), 
                                  size = 2) +
  scale_fill_brewer()

----
# loo significance testing
loo0 <- loo(fit)
loo1 <- loo(fit1)
loo2 <- loo(fit2)
loo_compare(loo1, loo2)
loo_compare(loo0, loo1)
